\documentclass[12pt,english]{simplecv}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{geometry}
\geometry{verbose,tmargin=.2in,bmargin=.2in,lmargin=.2in,rmargin=.2in}
\setcounter{secnumdepth}{0}
\setcounter{tocdepth}{0}
\usepackage{color}
\usepackage[unicode=true, 
pdfusetitle,
bookmarks=true,
bookmarksnumbered=false,
bookmarksopen=false,
breaklinks=true,
pdfborder={0 0 1},
backref=false,
colorlinks=true]
{hyperref}
\hypersetup{urlcolor=blue, linkcolor=blue, citecolor=blue}

\makeatletter

\makeatother

\usepackage{babel}
\begin{document}

\leftheader{Purok 4, Lunga, Valencia\\Negros Oriental 6215\\Philippines}

\rightheader{aubreymoore2013@gmail.com}

\title{Aubrey Moore}

\maketitle

\section{Education}
\begin{topic}
\item [{1988}]Ph.D., Entomology, University of Hawaii, Honolulu, Hawaii
\item [{1984}] M.S., Entomology, Michigan State University, East Lansing, Michigan
\item [{1979}] B.Sc., Integrated Science Studies, Carleton University, Ottawa, Ontario 
\end{topic}

\section{Professional Experience}
\begin{topic}
\item [{2008-2023}] Extension Entomologist, Cooperative Extension Service, University of Guam, Guam 
\item [{2003-2008}] Research Associate, College of Natural \& Applied Sciences, University of Guam, Guam 
\item [{1999-2003}] Pesticide Evaluator, Pest Management Regulatory Agency, Health Canada, Ottawa, ON
\item [{1998-1999}] Entomologist, School of Agriculture \& Life Sciences,
Northern Marianas College, Saipan 
\end{topic}

\section{Relevant Publications}

\begin{thebibliography}{10}	

\bibitem{} Moore, Aubrey. 2019. \textbf{YouTube Video: Training an Object Detector to Locate Coconut Palms Damaged or Killed by Coconut Rhinoceros Beetle.} \url{https://www.youtube.com/watch?v=zzSorqcmt9U}

\bibitem{} Moore, Aubrey, and Trevor Jackson. 2020. \textbf{Automated Roadside Video Surveys for Detecting and Monitoring Coconut Rhinoceros Beetle Damage to Coconut Palms.} Presented at the Annual Meeting of the CRB-G Action Group. \url{https://aubreymoore.github.io/crb-roadside-slides}

\bibitem{} Moore, Aubrey. 2020. \textbf{Using a Cell Phone and Artificial Intelligence to Map Coconut Rhinoceros Beetle Damage.} WPTRC Impact Report. Mangilao, Guam: Western Pacific Tropical Research Center, College of Natural and Applied Sciences, University of Guam. \url{https://www.uog.edu/_resources/files/wptrc/2020WPTRCFinal.pdf}

\bibitem{} Moore, Aubrey. 2023. \textbf{Webmaps showing results of automated roadside surveys of coconut rhinoceros beetle damage on Guam.} \url{https://aubreymoore.github.io/Guam-CRB-web-maps/}

\bibitem{} Moore, Aubrey. 2023. \textbf{Webmap showing results of an automated roadside survey on Majuro} \url{https://aubreymoore.github.io/Majuro-CRB-damage-map-1/webmap}

\bibitem{} Moore, Aubrey, Trevor Jackson, Roland Quitugua, Robert Bevacqua, Jonae Sayama, and Ross Miller. 2023. \textbf{Coconut Rhinoceros Beetle. US Forest Service, Forest Insect and Disease Leaflet 191.} \url{https://www.fs.usda.gov/foresthealth/docs/fidls/FIDL-191-CoconutRhinocerosBeetle.pdf}.


\end{thebibliography}

\end{document}
